### 2024-07-22 data-visualization.qmd
20240721 - fix bar plot

ggplot2::ggplot(
  data = player_stats_seasonal_offense %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = fantasy_points,
    fill = position_group
    )
) +
  geom_bar(
    stat = "identity",
    position = position_dodge(width = 0)) +
  theme_classic()
```

To display bars corresponding to a 95% confidence interval, we first compute summary statistics:

@@

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group
    )
) +
  geom_bar(
    stat = "identity",
    position = position_dodge(width = 0)) +
  geom_errorbar(
    aes(ymin = ci_lower, ymax = ci_upper),
    width = 0.2,
    position = position_dodge(width = 0)
  ) +
  theme_classic()
```

>>>>

To create a bar plot, we first compute summary statistics:

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary,
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  theme_classic()
```

@@

ggplot2::ggplot(
  data = player_stats_seasonal_offense_summary %>%
    filter(position_group %in% c("QB","RB","WR","TE")),
  mapping = aes(
    x = position_group,
    y = mean,
    fill = position_group,
    color = position_group
    )
) +
  geom_bar(
    stat = "identity") +
  geom_errorbar(
    aes(
      ymin = ci_lower,
      ymax = ci_upper),
    width = 0.2,
    color = "black"
  ) +
  theme_classic()
```
